Equivalence Testing and the Second Generation \emph{P}-Value

### 2019-04-11 manuscript.Rmd
Correction for most extreme case when equivalence range are -.99 and .99, and n = 4

@@

As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50%. Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv*100,3)`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range.

>>>>

```{r, include=FALSE}
low_eqbound_r = -0.99
high_eqbound_r = 0.99
res<-TOSTr(n = 4,
           r = 0.99,
           low_eqbound_r = low_eqbound_r,
           high_eqbound_r = high_eqbound_r,
           alpha = .05,
           plot = FALSE,
           verbose = FALSE)
sgpv2 <- p_delta(res$LL_CI_TTEST,res$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
```

@@

As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50%. Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv*100,3)`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% [UNTRUE: this is about 36% of the observed correlations... once again, due to asymmetric CI around r] of the correlations observed in the future will fall in this range.

### 2019-04-11 manuscript.tex
Correction for most extreme case when equivalence range are -.99 and .99, and n = 4

If the observed correlation falls exactly on the equivalence bound the \emph{p}-value for the equivalence test is 50\%. In correlation test, the \emph{p} value is computed based on a transformed correlation score, computd as follows:

@@

As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation \emph{p}-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50\%. Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from 0.11 to 0.70) according to Blume et al. (2018) 58.11\% of the data-supported hypotheses are null hypotheses, and therefore 58.10\% of the data-supported hypotheses are compatible with the null premise. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 58.10\% of the confidence interval overlaps with the equivalence range, even though in the long run only 50\% of the correlations observed in the future will fall in this range.

It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answers, and the question a \emph{p}-value answers. The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{} 0.975 in an equivalence test, since the SGPV and \emph{p}-value for the TOST procedure are always directly related at these values. Although Blume et al. (2018) state that \enquote{the degree of overlap conveys how compatible the data are with the null premise} this definition of what the SGPV provides does not hold for asymmetric confidence intervals. Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as \enquote{compatibility with the null hypothesis}. Indeed, Blume and colleagues write in the supplemental material that \enquote{The magnitude of an inconclusive second-generation \emph{p}-value can vary slightly when the effect size scale is transformed. However definitive findings, i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale changes.}

>>>>

If the observed correlation falls exactly on the equivalence bound the \emph{p}-value for the equivalence test is 50\%. In correlation test, the \emph{p} value is computed based on a transformed correlation score, computed as follows:

@@

As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation \emph{p}-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50\%. Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from 0.60 to 1) according to Blume et al. (2018) 58.11\% of the data-supported hypotheses are null hypotheses, and therefore 58.10\% of the data-supported hypotheses are compatible with the null premise. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 50\% of the correlations observed in the future will fall in this range.

It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, and in the same way of thinking, the probability of observing a correlation smaller or larger than the true correlation is also closer to 0.5.

The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{} 0.975 in an equivalence test, since the SGPV and \emph{p}-value for the TOST procedure are always directly related at these values. Although Blume et al. (2018) state that \enquote{the degree of overlap conveys how compatible the data are with the null premise} this definition of what the SGPV provides does not hold for asymmetric confidence intervals. Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as \enquote{compatibility with the null hypothesis}. Indeed, Blume and colleagues write in the supplemental material that \enquote{The magnitude of an inconclusive second-generation \emph{p}-value can vary slightly when the effect size scale is transformed. However definitive findings, i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale changes.}
